Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
more on experimental eval

\usepackage{booktabs} % For formal tables
\usepackage{graphicx}
\usepackage{autobreak}
\usepackage{mytodonotes}
\usepackage{subcaption}
\usepackage[ruled,vlined]{algorithm2e}
%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{cleveref}

@@

First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
  called \emph{collect the items} -- see \Cref{fig:env}.
%
This environment consists of a 2D euclidean space in which a variable number of \emph{items} and \emph{agents} 
 are randomly placed.
%
The goal of the agents is to cooperate to collect all the items in the smallest amount of time possible. 
%
% Action space
%
% Obseration space

@@

% \begin{itemize}
% \item Introduce the custom "collect the items" multi-agent environment:
% \begin{itemize}
% \item Describe the environment's dynamics, agent goals, and challenges.
% \item Specify the action space (continuous and discrete) and observation space design.
% \item Explain the reward structure, emphasizing the components that encourage cooperation.
% \end{itemize}
% \item Detail the implementation framework (Gymnasium, RLlib, PyTorch).
% \item Specify the chosen RL algorithm (DQN) and its hyperparameter configuration.
% \item Define the evaluation metrics: average episode length and average reward.
% \end{itemize}

>>>>

\usepackage{booktabs} % For formal tables
\usepackage{graphicx}
\usepackage{autobreak}
\usepackage{mytodonotes}
\usepackage{subcaption}
\usepackage[inline]{enumitem}
\usepackage[ruled,vlined]{algorithm2e}
%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{cleveref}

@@

First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
  called \emph{collect the items} -- see \Cref{fig:env}.
%
This environment consists of a 2D euclidean space in which a variable number of \emph{items} and \emph{agents} 
 are randomly placed.
%
The goal of the agents is to cooperate to collect all the items in the smallest amount of time possible. 
%
In particular, each agent has an observation space defined by three main parameters, namely: 
\begin{enumerate*}[label=(\roman*)]
  \item number of closest agents that the agent is able to see (thus, forming a neighborhood);
  \item number of closest items that the agent is able to see;
  \item memory of past states, thus encoding also temporal information, helping each agent to understand 
    the evolution of the environment.
\end{enumerate*} 
%
Regarding the action space, each agent has $8$ possible moves, namely the possible direction on a grid 
  (up, down and diagonal).

% Reward

% Specify the chosen RL algorithm (DQN) and its hyperparameter configuration

% Define the evaluation metrics: average episode length and average reward

@@

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/behavior.pdf}
  \caption{TODO
  }
  \label{fig:behavior}
\end{figure}
